% Source notes. Where the originals came from and how the transcription
% was assembled. One paragraph per source.

\cleardoublepage
\thispagestyle{laplain}
\vspace*{0.10\textheight}
\begin{center}
    \eyebrow{Source Notes}\par
    \vspace{0.4em}
    \brassrule[36pt]\par
\end{center}
\vspace{2em}

\noindent
% TODO[blake]: write one paragraph per item, in plain past tense.

\paragraph{The 2022 family zip.}
\textsc{[\,placeholder \,---\, who scanned the originals, where the originals were
held, what was in the zip when it arrived, what was missing, what was
mislabeled. Name the family member who did the work.\,]}

\paragraph{The 23-page family PDF.}
\textsc{[\,placeholder \,---\, who typed the early transcriptions before you began
this project, what their conventions were, and how those transcriptions
were carried forward into the volume.\,]}

\paragraph{The iPhone rescans (2026).}
\textsc{[\,placeholder \,---\, when you rescanned the originals on your phone,
why, what improvements those scans made over the 2022 zip, and how the
new scans were named and sessioned.\,]}

\paragraph{Biographical research.}
\textsc{[\,placeholder \,---\, the 25-page biographical research document, who
prepared it, what archives or interviews it drew on.\,]}

\paragraph{Press coverage.}
\textsc{[\,placeholder \,---\, WKYT's February 15, 2023 segment on the letters,
what the segment said, and who else has written about the collection.\,]}

\paragraph{Conventions in the transcriptions.}
This volume preserves Gene's original spelling, punctuation, and
abbreviations. Uncertain readings of single words are marked
\textsc{[?]}. Editor's footnotes are marked with an asterisk and printed
at the foot of the page. Square brackets in the body, where they
appear, indicate words supplied by the editor to complete a torn or
illegible line. Where Gene signed twice, both signatures are
preserved.
\vfill
